Introduction

### 2015-07-15 dissertation/motivation.tex
most of motivation

The overarching problem is that even though each of these problems are
rarely encountered, there are so many such problems, that we encounter
them all the time. I would like to see a Semantic Web where the
plumber delivers his offer in a manner so that the open options can be
distinguished from the constraints, where a query can be formulated to
find the area I'd like to build my house based on such extensive
criteria, where the very rare comparison between a collapsed baby
stroller and car trunk can be done, where I will be able to cook
better food without being a chef and where I can book my travel based
on what I want to experience rather than make me choose a destination
based on lacking information.

@@

>>>>

Of fundamental importance is that is that even though each of these
problems are rarely encountered, there are so many such problems that
we encounter them frequently. I would like to see a Semantic Web
where the plumber delivers his offer in a manner so that the open
options can be distinguished from the constraints, where a query can
be formulated to find the area I'd like to build my house based on
such extensive criteria, where the very rare comparison between a
collapsed baby stroller and car trunk can be done, where I will be
able to cook better food without being a chef and where I can book my
travel based on what I want to experience rather than make me choose a
destination based on lacking information.

@@

Moreover, the problem could be solved by writing programs to integrate
the variety of data sources for each scenario, but this is clearly not
sustainable, as each particular integration is of interest to very
few, but the cost of the integration increases for every integration
task. Fewer people to pay for a more expensive task quickly becomes
economically infeasible.

Technically, it might be an easier problem to solve if the data could
be centralized, and that solution has been argued by
\cite{DBLP:conf/semweb/BetzGHS12}. Nevertheless, even if all their
arguments remain valid from a technical viewpoint, the most important
arguments against centralisation are social: If important components
of the Semantic Web is under the control of some central authority, it
is likely that one cannot publish anything, link to anything, or
develop any application without permission. It may create an unhealthy
power structure, which may create commercial or intellectual
hegemonies. Tim Berners-Lee discussed this in \cite{TODO} and an
interview in Wired Magazine in 2014\footnote{see
  \href{http://www.wired.co.uk/news/archive/2014-02/06/tim-berners-lee-reclaim-the-web}}.
This is the key motivation to still design a distributed Semantic Web,
regardless of the technical difficulties that may arise.

The naive enthusiast may now forward the claim that Linked Data is the
solution and the whole solution, and at times of hubris, I may myself
have been guilty of conjecturing that sitting down to write the code
based on what we already know would solve the problem.

At times of doubt, the large number of unsolved problems, theoretical
as well as practical become apparent. In the following, I will try to
enumarate the problems I have foreseen, discuss their place in current
research, and what problems I have attempted to tackle in this
dissertation.

%%  LocalWords:  hegemonies
